Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-23 ms/manuscript.Rmd
Fix p-value calculations for randomizations

# PE rank
b <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs_rank)) +
  geom_sf(color = "transparent") +
  labs(fill = "Rank PE") +
  scale_fill_scico(palette = "lajolla") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme() +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

@@

```{r diversity-by-cluster, fig.width = 7, fig.height = 7}
data <-
ses_div_ferns_spatial %>%
  filter(taxonomic_cluster %in% c(1,2,3,4)) %>%
  as_tibble %>%
  select(pd_obs_z, rpd_obs_z, fd_obs_z, rfd_obs_z, pe_obs_rank, taxonomic_cluster)

@@

e <- ggplot(data, aes(x = taxonomic_cluster, y = pe_obs_rank)) +
  geom_jitter(aes(color = taxonomic_cluster)) +
  scale_color_manual(values = cluster_cols, breaks = 1:4) +
  geom_boxplot(color = "grey80", fill = "transparent", outlier.shape = NA, alpha = 0.25) +
  labs(
    y = "Rank PE",
    x = "Cluster",
    color = "Cluster"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank(),

@@

**`r figure("div-by-tax-region")`**. `r figure_cap("div-by-tax-region")`. **A**, Standard effect size (SES) of phylogenetic diversity (PD). **B**, SES of relative PD (RPD). **C**, SES of functional diversity (FD). **D**, SES of relative FD (RFD). **E**, rank of observed phylogenetic endemism (PE) out of 999 random communities. Only top four clusters with the most sites shown.

>>>>

# PE p-value
b <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs_p_upper)) +
  geom_sf(color = "transparent") +
  labs(fill = "PE p-score") +
  scale_fill_scico(palette = "lajolla") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme() +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

@@

```{r diversity-by-cluster, fig.width = 7, fig.height = 7}
data <-
ses_div_ferns_spatial %>%
  filter(taxonomic_cluster %in% c(1,2,3,4)) %>%
  as_tibble %>%
  select(pd_obs_z, rpd_obs_z, fd_obs_z, rfd_obs_z, pe_obs_p_upper, taxonomic_cluster)

@@

e <- ggplot(data, aes(x = taxonomic_cluster, y = pe_obs_p_upper)) +
  geom_jitter(aes(color = taxonomic_cluster)) +
  scale_color_manual(values = cluster_cols, breaks = 1:4) +
  geom_boxplot(color = "grey80", fill = "transparent", outlier.shape = NA, alpha = 0.25) +
  labs(
    y = "PE p-score",
    x = "Cluster",
    color = "Cluster"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank(),

@@

**`r figure("div-by-tax-region")`**. `r figure_cap("div-by-tax-region")`. **A**, Standard effect size (SES) of phylogenetic diversity (PD). **B**, SES of relative PD (RPD). **C**, SES of functional diversity (FD). **D**, SES of relative FD (RFD). **E**, p-score of observed phylogenetic endemism (PE) relative to 999 random communities. Only top four clusters with the most sites shown.
